The SMT Competition 2015--2018

### 2019-09-02 2018/report/SMT-COMP.tex
Minor

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-sat} answers (out
      of \num{30370517} total) within a time limit of \SI{2400}{s} on
      common benchmarks 2015--2018 of all divisions in the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all divisions in the \ucoretrack.\\${}$}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}

@@

\paragraph{The Next Competition}

At the time of writing, the 2019 iteration of the competition has just come to a close. It was too late to be included in this report but certain changes were made, partly influenced by the writing of this report. The three main changes were:
\begin{itemize}
    \item \emph{Additional Scores.} This report made it clear that simply looking at the number of problems solved was a simplified view. In 2019 the competition introduced new \emph{additional scores} for
    satisfiable/unsatisfiable benchmarks and benchmarks solved within 24
    seconds in the \maintrack. Organising results by satisfiability is not new. The SAT competition previously split satisfiable and unsatisfiable benchmarks into separate tracks, but merged them completely from 2016. The CASC competition separates \emph{theorems} and \emph{non-theorems} for most tracks. However, other competitions do not tend to look at short time limits (CASC had the SLH division in 2017).

  \item \emph{Benchmarks.}  Partly to combat the growing size of SMT-LIB, and partly to inject more competition-like variability and focus into the results, in 2019 the competition removed \emph{non-competitive divisions} and then filtered
    benchmarks to exclude those seen as \emph{trivial} (taken as those solved
    by all competitors in the previous competition in less than 1 second). This brings it closer to the CASC competition where a small subset of problems are chosen based on difficultly, although there was no inclusion of a difficultly measure in benchmark selection beyond the initial filtering. The SAT competition takes a different approach to benchmark selection with a \emph{bring your own benchmark} approach.

\item \emph{Competition-Wide Scoring.} Motivated by the need to avoid competition-wide scoring becoming overly focussed on the \emph{breadth} of a solver, in 2019 the competition replaced the notion of \emph{competition-wide scoring} with awards that do not attempt to compare divisions. Two awards were introduced -- the \emph{Largest Contribution} award looked at the contribution a solver made to the virtual best solver, and the \emph{Biggest Lead} award measured the distance between the winner and second place. No other competition (that we are aware of) attempts to rank solvers across multiple areas in this way. However, the CASC competition does have a notion of \emph{State of the Art Contribution}, similar to the largest contribution measure.

\end{itemize}
Other changes include
\begin{itemize}

	\item the inclusion of {\tt check-sat} commands with unknown status in
  the \apptrack,

  \item the introduction of a new experimental \emph{model validation track}
    with a single QF\_BV division where the models produced by solvers are
    checked,
  \item the introduction of a new \emph{industrial challenge track} consisting
    of unsolved benchmarks submitted specifically for the track.
\end{itemize}

\paragraph{The Future}

Looking to the future of the competition, it is clear that further development should be undertaken with care,
keeping in mind that major changes require not just the competition
organizers, but also participants to adapt.

>>>>

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-\allowbreak sat}
      answers (out of \num{30370517} total) within a time limit of
      \SI{2400}{s} on common benchmarks 2015--2018 of all divisions in
      the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all divisions in the \ucoretrack.\\${}$}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}

@@

\paragraph{The Next Competition}
%
At the time of writing, the 2019 iteration of the competition has just
come to a close.  It was too late to be included in this report but
certain changes were made, partly influenced by the writing of this
report.  The three main changes were:
\begin{itemize}
\item \emph{Additional Scores.}  This report made it clear that simply
  looking at the number of problems solved was a simplified view.  In
  2019 the competition introduced new \emph{additional scores} for
  satisfiable/unsatisfiable benchmarks and benchmarks solved within 24
  seconds in the \maintrack.  Organizing results by satisfiability is
  not new.  The SAT competition previously split satisfiable and
  unsatisfiable benchmarks into separate tracks, but merged them
  completely from 2016.  The CASC competition separates
  \emph{theorems} and \emph{non-theorems} for most tracks.  However,
  other competitions do not tend to look at short time limits (CASC
  had the SLH division in 2017).
\item \emph{Benchmarks.}  Partly to combat the growing size of
  SMT-LIB, and partly to inject more competition-like variability and
  focus into the results, in 2019 the competition removed
  \emph{non-competitive divisions} and then filtered benchmarks to
  exclude those seen as \emph{trivial} (taken as those solved by all
  competitors in the previous competition in less than 1 second).
  This brings it closer to the CASC competition where a small subset
  of problems are chosen based on difficulty, although there was no
  inclusion of a difficulty measure in benchmark selection beyond the
  initial filtering.  The SAT competition takes a different approach
  to benchmark selection with a \emph{bring your own benchmark}
  approach.
\item \emph{Competition-Wide Scoring.}  Motivated by the need to avoid
  competition-wide scoring becoming overly focused on the
  \emph{breadth} of a solver, in 2019 the competition replaced the
  notion of \emph{competition-wide scoring} with awards that do not
  attempt to compare divisions.  Two awards were introduced---the
  \emph{Largest Contribution} award looked at the contribution a
  solver made to the virtual best solver, and the \emph{Biggest Lead}
  award measured the distance between the winner and second place. No
  other competition (that we are aware of) attempts to rank solvers
  across multiple areas in this way.  However, the CASC competition
  does have a notion of \emph{State of the Art Contribution}, similar
  to the largest contribution measure.
\end{itemize}
Other changes included
\begin{itemize}
\item the inclusion of {\tt check-sat} commands with unknown status in
  the \apptrack,
\item the introduction of a new experimental \emph{model validation
  track} with a single QF\_BV division where the models produced by
  solvers are checked,
\item the introduction of a new \emph{industrial challenge track}
  consisting of unsolved benchmarks submitted specifically for the
  track.
\end{itemize}

\paragraph{The Future}
%
Looking to the future of the competition, it is clear that further
development should be undertaken with care, keeping in mind that major
changes require not just the competition organizers, but also
participants to adapt.
